Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd

+ <span style = "color: blue;"> As mentioned in my previous review, the term "economically optimal" has different meanings among agricultural economists. The new footnote (footnote 1 on p. 5) is appreciated, but here you should specify that "economically optimal" in the context of the article does not mean "socially optimal."</span>

Response:

+ <span style = "color: blue;"> None of the figure numbers appear in the text; instead, each figure reference is followed by "Error! Reference source not found." These all should be corrected. </span>

Response: We apologize for the figure number errors. Those were generated by the online PDF compiling tool of JAAEA submision website. We will communicate with the journal editor and technician to solve the errors.

@@

+ <span style = "color: blue;">P. 12, line 229: Given that JAAEA is an economics journal and not an agronomy journal, you should rewrite "Latin square trial design schema" as "trial design" here, and at the end of the next sentence, write "each column of the block (i.e., a Latin square)." </span>

Response: We followed your suggestions and texts were modified accordingly.

+ <span style = "color: blue;">P. 14, line 254: For additional clarity, you could point out that the EONR rate is just the value of N that solves $\\cdot f(N) - \omega\dcot N$, where $f(N)$ is SCAM-estimated. </span>

Response: Here at the beginning of this session, we only briefly introduce the procedure of estimating uniform EONR. The more detailed explanation of how EONR is calculated by solving for maximization of p\cdot \hat{f}^{SCAM} (N)-w\cdot N was described in the later part (see line 281??)

@@

+ <span style = "color: blue;">PP. 22-23, lines 439-441: This sentence should be removed because it seems speculative. More importantly, researchers do not "have" to implement a methodology because it is conveniently available in standard software; instead, they could code their own models, methods, etc.  </span>

Response: There is no speculation in this sentence. We are stating a drawback of linear-plateau model. What we state is a irrefutable fact and important in real world practice of estimating yield response function.

+ <span style = "color: blue;">P. 33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440). Also add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).  </span>

Response: We added the following details to the Figure 2 notes: "The experimental field contains a total of 288 N trial plots, arranged in 24 rows $\times$ 12 columns. Each N plot contains 5 effective yield subplots (as illustrated in Figure 1, Panel b), and the total number of subplots is 1,440. The total number of effective cells are 8,640 (72 rows $\times$ 120 columns)".

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd

**Response**: Ignored as suggested.

4. <span style = "color: blue;"> The authors generate the "true" site-specific parameters using a Gaussian random field. It does not appear that the authors allowed correlations between the model parameters. In practice, response parameters are typically correlated. How does this affect the simulation results? It is unclear if the simulated random field ensured that parameters of the linear and quadratic n-rates were constrained to be positive and negative, respectively. How was this verified?</span>

**Response**:

This comment clearly shows that this reviewer did not pay attention to our replies to his comments (the first round review, comment 1). In our reply to his comments, we clearly stated that the site-specific parameters are indeed spatially correlated. We also ensured that the coefficients on the linear and quadratic N-rates were constrained to be positive and negative. This is not a hard task. We share all the codes written in R on a publicly accessible repository. Anybody can check how this was done in our paper.

@@

5. <span style = "color: blue;">Page 11, Line 206: was this random field generated once and then used for 1,000 MC iterations, or was the field generated for each MC iteration? What about the errors? What were the nugget, sill, etc., for each simulated parameter?  </span>

**Response**:

Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance. However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.

Clarifying sentences were added to page ??, line ??.

@@

6. <span style = "color: blue;">Replicability. How would one proceed if one were to replicate what the authors did? For example, "Note that the range of the optimal N rates of individual rounds were narrower." What does this mean? Yield Data generation. What distribution were the e's? The Methods need to be more clearly documented if others want to replicate the study.</span>

**Response**:

We agree that we can provide more information on how the data is generated. The error term follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).

### 2023-11-05 Writing/manuscript_gwr.rmd
more replies

The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation]. The simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells. The choice of 600m range in this study was based on empirical data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. The magnitude of the error term $\varepsilon_{j, i}$ was also based on the DIFM project empirical data. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

>>>>

The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation]. The simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells. The choice of 600m range in this study was based on empirical data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. The magnitude of the error term $\varepsilon_{j, i}$ was also based on the DIFM project empirical data. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms. Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of EONR for each simulation instance. However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.
